Articles_Plots

### 2022-02-01 Articles.Rmd
update article rmd with colors

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("RM",paste0("AM ",1:3),"MF")

@@

Identical_ro$Model<-factor(Identical_ro$Model,
                           levels = c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                      "OSMAC mMSE RM","OSMAC mMSE AM 1","OSMAC mMSE AM 2","OSMAC mMSE AM 3",
                                      "OSMAC mVc RM", "OSMAC mVc AM 1", "OSMAC mVc AM 2","OSMAC mVc AM 3",
                                      "OSMAC mMSE MF","OSMAC mVc MF"))

Selected_Models_mMSE<-c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                        "OSMAC mMSE RM","OSMAC mMSE AM 1","OSMAC mMSE AM 2","OSMAC mMSE AM 3",
                        "OSMAC mMSE MF")

Colors_mMSE<-c("#FFC4D8", "#E28490","#BB2C3E","#55141C",
               "#88CCEE", "#A6C3D3","#5D92B0","#35586C", 
               "#DDCC77")

Selected_Models_mVc<-c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                       "OSMAC mVc RM", "OSMAC mVc AM 1", "OSMAC mVc AM 2","OSMAC mVc AM 3",
                       "OSMAC mVc MF")

Colors_mVc<-Colors_mVc<-c("#FFC4D8","#E28490","#BB2C3E","#55141C", 
                          "#88CCEE","#A6C3D3","#5D92B0","#35586C", 
                          "#DDCC77")

>>>>

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("RM",paste0("AM ",1:3),"MR")

@@

Identical_ro$Model<-factor(Identical_ro$Model,
                           levels = c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                      "OSMAC mMSE RM","OSMAC mMSE AM 1","OSMAC mMSE AM 2","OSMAC mMSE AM 3",
                                      "OSMAC mVc RM", "OSMAC mVc AM 1", "OSMAC mVc AM 2","OSMAC mVc AM 3",
                                      "OSMAC mMSE MR","OSMAC mVc MR"))

Selected_Models_mMSE<-c("RS RM",#"RS AM 1","RS AM 2","RS AM 3",
                        "OSMAC mMSE RM","OSMAC mMSE AM 1","OSMAC mMSE AM 2","OSMAC mMSE AM 3",
                        "OSMAC mMSE MR")

Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
               "#FFC4D8", "#E28490","#BB2C3E","#55141C",
               "#DDCC77")

Selected_Models_mVc<-c("RS RM",#"RS AM 1","RS AM 2","RS AM 3",
                       "OSMAC mVc RM", "OSMAC mVc AM 1", "OSMAC mVc AM 2","OSMAC mVc AM 3",
                       "OSMAC mVc MR")

Colors_mVc<-Colors_mVc<-c("#88CCEE",#"#A6C3D3","#5D92B0","#35586C", 
                          "#FFC4D8","#E28490","#BB2C3E","#55141C", 
                          "#DDCC77")
